SDR enhancement by clouds

### 2024-03-05 article/article.Rmd
Commit 2024-03-05 18:24

```{r echo=FALSE, fig.cap="Distribution of CE above reference"}
knitr::include_graphics("../images/distributions-5.png")
```

>>>>

<!-- ```{r echo=FALSE, fig.cap="Distribution of CE above reference"} -->
<!-- knitr::include_graphics("../images/relative_distributions-2.png") -->
<!-- ``` -->

```{r echo=FALSE, fig.cap="Distribution of CE above reference"}
knitr::include_graphics("../images/relative_distributions-4.png")
```
